I/O simulation model with Linux page cache, integration and evaluation in SimGrid framework

### 2020-12-02 paper_io_sim.tex
comments on results

			In simulated platform description, because the disk bandwidths in SimGrid 
			are symmetrical, we measure the read/write bandwidths on our cluster and 
			take the average bandwidths. 
			As the pipelines are single-core, we create simulated tasks, 
			each of them runs on only one core. 
			While in Python, computation time can be directly configured, 
			this time is injected to the WRENCH simulators with number of flops, 
			which is calculated with CPU speed and compute duration. 
			In our experiments, the CPU speed is set to 1 Gflops. 
			Finally, because WRENCH simulates applications base on network-communication, 
			we use an infinite bandwidth to eliminate network latency for local I/Os.
			The details of simulated platform and the source code of the simulator 
			are available here: 
			\url{https://github.com/wrench-project/wrench/tree/master/examples/basic-examples/io-pagecache}

@@

			The pipeline used in this experiment consists of three tasks, 
			each task reads a file, increases every byte and writes output file 
			to local disk. 
			We use the input sizes of 20~GB, 50~GB, 75~GB, 100~GB and run 
			the pipeline on the cluster.
			The pipeline is simulated with the Python prototype simulator, 
			original WRENCH and WRENCH-Ext simulator.

@@

	\section{Results}
	\label{results}			
		The benchmark results of bandwidths and the values used in the simulators 
		in our all experiments are shown in \ref{table:benchmark}.

		\begin{table}
		\centering
		\begin{tabular}{|l|c|c|c|}
		\hline
			Bandwidths (MBps)  & Cluster (real) & Python simulator & WRENCH simulator\\
		\hline
			Memory read  & 6860	& 4812	 & 4812\\
			Memory write & 2764	& 4812 & 4812\\
			Local disk read & 510 & 465 & 465\\
			Local disk write & 420 & 465	 & 465\\
			Remote disk read & 515 & - & 445\\
			Remote disk write & 375 & - & 445\\
			Network bandwidth & 3000 & - & 3000\\
		\hline
		\end{tabular}
		\caption{Bandwidth benchmark results and simulator configurations}
		\label{table:benchmark}
		\end{table}

@@

			Memory behaviors of real pipeline execution and simulators are recorded 
			and the memory profiling results with 20GB and 100GB input files 
			are illustrated in Figure~\ref{fig:single_memprof}. 
			The bars in the figures present activities in tasks (read, compute and write), 
			while the lines describe memory status throughout run time of the pipeline. 
			Because the results with 20Gb, 50GB, 100GB are analogous, we only include 
			the results with 20GB and 100GB in this paper.

			As shown in the figures, the makespans of the simulated pipeline are 
			close to the makespan of the real execution with similar patterns of I/O time 
			real execution and simulation. 
			But more importantly, with all input sizes, similar trends can also be found 
			in the lines describing memory status in simulators and the real execution. 
			The akin movements of amount of cache used (purple lines) in reality 
			and simulation show that the use of page cache is well reproduced by the simulators. 
			The amount of dirty data ( red lines) also follow similar trends, 
			which means not only the amount dirty data, but also the flushing and 
			periodical flushing mechanisms are accurately modeled in our simulators. 
			This can be seen in in the increase of the amount of dirty data during the writes 
			and the decrease during the reads and computations. 
			According to the results achieved with all input sizes in the experiment, 
			we can observe identical trends in reality and simulation with 20GB, 
			50GB and 75GB input files. However, with 100GB input file, 
			the third read is not correctly simulated, leading to longer simulated time 
			than in real execution. This will be explained later in this section.

@@

			\begin{figure*}
			\centering
			\begin{subfigure}{\linewidth}
				\centering
   				\includegraphics[width=\linewidth]{result/single/figures/single_memprof.pdf}
			\end{subfigure}
			\caption{Memory profiling results with different input file sizes}
			\label{fig:single_memprof}	
			\begin{subfigure}{\linewidth}
				\centering
   				\includegraphics[width=\linewidth]{result/single/figures/single_errors.pdf}
			\end{subfigure}
			\caption{Simulation errors with different input file sizes}
			\label{fig:single_error}	
			\begin{subfigure}{\linewidth}
				\centering
   				\includegraphics[width=\linewidth]{result/single/figures/cached_files.pdf}
			\end{subfigure}	
			\label{fig:single_cache}
   			\caption{Amount of file data in cache after each I/O activity with 100GB of input}
			\end{figure*}

@@

	\section{Discussion and Future Work}
	\label{discussion}			
			In computing infrastructures, especially those use for data-intensive applications, 
			page cache undoubtedly has certain impacts on performance. 
			Conducting simulation experiments is an effective approach to predict, 
			evaluate the performance of not only application, scheduler but also 
			infrastructure settings. 
			Unfortunately, page cache is missing in many simulation tools for HPC systems. 
			In this study, we proposed a simulation model of I/O with page cache, 
			implement it with SimGrid using WRENCH, and evaluate the results 
			with different experiments. 
			The results shows our achievements in terms of simulation accuracy 
			and the application potential in practice. 
			On the other hands, the model exposed some limitations that can be 
			further improved.

>>>>

			In simulated platform description, because the disk bandwidths in SimGrid 
			are symmetrical, we measure the read/write bandwidths on our cluster and 
			take the average bandwidths. 
			As the pipelines are single-core, we create simulated tasks, 
			each of them runs on only one core. 
			While in Python, computation time can be directly configured, 
			this time is injected to the WRENCH simulators with number of flops, 
			which is calculated with CPU speed and compute duration. 
			In our experiments, the CPU speed is set to 1 Gflops. 
			Finally, because WRENCH simulates applications base on network-communication, 
			we use an infinite bandwidth to eliminate network latency for local I/Os.
			The details of simulated platform and the source code of the simulator 
			are available here: 
			\url{https://github.com/wrench-project/wrench/tree/master/examples/basic-examples/io-pagecache}
			\tristan{Our experiments use commit abcd}

@@

			The pipeline used in this experiment consists of three tasks, 
			each task reads a file, increases every byte and writes output file 
			to local disk. 
			We use the input sizes of 20~GB, 50~GB, 75~GB, 100~GB and run 
			the pipeline on the cluster.
			The pipeline is simulated with the Python prototype simulator, 
			original WRENCH and WRENCH-Ext simulator \tristan{name your simulator something 
			that refers to page cache, maybe WRENCH-cache}.

@@

	\section{Results}
	\label{results}			
		The benchmark results of bandwidths and the values used in the simulators 
		in our all experiments are shown in Table~\ref{table:benchmark} \tristan{This isn't results, it should go in II.C, 
		next to the paragraph where you talk about symmetrical bandwidths}.

		\begin{table}
		\centering
		\begin{tabular}{|l|c|c|c|}
		\hline
			Bandwidths (MBps)  & Cluster (real) & Python simulator & WRENCH simulator\\
		\hline
			Memory read  & 6860	& 4812	 & 4812\\
			Memory write & 2764	& 4812 & 4812\\
			Local disk read & 510 & 465 & 465\\
			Local disk write & 420 & 465	 & 465\\
			Remote disk read & 515 & - & 445\\
			Remote disk write & 375 & - & 445\\
			Network bandwidth & 3000 & - & 3000\\
		\hline
		\end{tabular}
		\caption{Bandwidth benchmark results and simulator configurations \tristan{add a sentence of explanation. Make the table fit in 1 column}}
		\label{table:benchmark}
		\end{table}

@@

			Memory behaviors of real pipeline execution and simulators are recorded 
			and the memory profiling results with 20GB and 100GB input files 
			are illustrated in Figure~\ref{fig:single_memprof} \tristan{convoluted writing}. 
			The bars in the figures present activities in tasks (read, compute and write), 
			while the lines describe memory status throughout run time of the pipeline \tristan{move any description of graphical features to the figure caption}. 
			Because the results with 20Gb, 50GB, 100GB are analogous, we only include 
			the results with 20GB and 100GB in this paper \tristan{analogous is not the right word}.

			As shown in the figures, the makespans of the simulated pipeline are 
			close to the makespan of the real execution with similar patterns of I/O time 
			real execution and simulation. 
			But more importantly, with all input sizes, similar trends can also be found 
			in the lines describing memory status in simulators and the real execution. 
			The similar evolutions of amount of cache used (purple lines) in reality 
			and simulation show that the use of page cache is well reproduced by the simulators. 
			The amount of dirty data ( red lines) also follow similar trends, 
			which means not only the amount dirty data, but also the flushing and 
			periodical flushing mechanisms are accurately modeled in our simulators. 
			This can be seen in in the increase of the amount of dirty data during the writes 
			and the decrease during the reads and computations. 
			According to the results achieved with all input sizes in the experiment, 
			we can observe identical trends in reality and simulation with 20GB, 
			50GB and 75GB input files. However, with 100GB input file, 
			the third read is not correctly simulated, leading to longer simulated time 
			than in real execution. This will be explained later in this section.

@@

			\begin{figure*}
			\centering
			\begin{subfigure}{\linewidth}
				\centering
   				\includegraphics[width=\linewidth]{result/single/figures/single_memprof.pdf}
			\end{subfigure}
			\caption{Memory profiling results with different input file sizes \tristan{put the simulation/real conditions on the side, make them larger and use the same color code as below (pink for real, etc). Put the memory values on top, similar to how they are in the graphs below. }}
			\label{fig:single_memprof}	
			\begin{subfigure}{\linewidth}
				\centering
   				\includegraphics[width=\linewidth]{result/single/figures/single_errors.pdf}
			\end{subfigure}
			\caption{Simulation errors with different input file sizes}
			\label{fig:single_error}	
			\begin{subfigure}{\linewidth}
				\centering
   				\includegraphics[width=\linewidth]{result/single/figures/cached_files.pdf}
			\end{subfigure}	
			\label{fig:single_cache}
   			\caption{Amount of file data in cache after each I/O activity with 100GB of input \tristan{Make a grouped histogram (1 histogram with two bars, one for real, one for simulation). Add a grouped histogram for 20GB. Use the same color code everywhere: real should be pink.}}
			\end{figure*}

@@

	\section{Discussion and Future Work}
	\label{discussion}			
			In computing infrastructures, especially those use for data-intensive applications, 
			page cache undoubtedly has certain impacts on performance. 
			Conducting simulation experiments is an effective approach to predict, 
			evaluate the performance of not only application, scheduler but also 
			infrastructure settings. 
			Unfortunately, page cache is missing in many simulation tools for HPC systems. 
			In this study, we proposed a simulation model of I/O with page cache, 
			implement it with SimGrid using WRENCH, and evaluate the results 
			with different experiments. 
			The results shows our achievements in terms of simulation accuracy 
			and the application potential in practice \tristan{what do you conclude? can we use your simulator to study big data applications on hpc clusters? under what conditions?}. 
			On the other hands, the model exposed some limitations that can be 
			further improved.
